---
title: "STAT253 - Homework#1"
author: "Sukru Gumustas - 150114032"
date: "21.03.2017"
output: word_document
---

##Answers to the Questions

```{r, echo=FALSE}
#First, I have to import the file. Before importing the file, I should import the "readr" library. I imported the CSV file by using the menu on the right. I also have to include "MASS" library to draw dotplot.
library(readr)
library(MASS)
fileLocation = "~/R/HW1/HW1_Dataset.csv"
myDataSet <- read_csv(fileLocation, col_names = FALSE, col_types = cols(X1 = col_double()), skip = 1)
```
#a) The mean (x) of the sample. Mean is calculated by using "mean" function in R.

```{r, echo=FALSE}
meanOfSample = mean(myDataSet$X1)
meanOfSample
```
#b) The variance (s^2) of the sample. It is calculated by using "var" function.
```{r, echo=FALSE}
variance = (var(myDataSet$X1)*100)/99
variance
```
#c) The standard deviation is calculated by both ways. First way is taking square root of variance. Second way is using "sd" function. Both calculations are below.
#SD calculated by variance is
```{r, echo=FALSE}
sdFromVariance = variance^(0.5)
sdFromVariance
```
#SD calculated by function is
```{r, echo=FALSE}
sdFromFunction = (sd(myDataSet$X1)*10)/(99^(0.5))
sdFromFunction
```
#d) To find lower and upper quartiles, I use "quantile" function.
#Lower quartile is
```{r, echo=FALSE}
lowerQuartile = quantile(myDataSet$X1, probs = 1/4)
lowerQuartile
```
#Upper quartile is
```{r, echo=FALSE}
upperQuartile = quantile(myDataSet$X1, probs=3/4)
upperQuartile
```
#e) To find maximum value, we use "max" function; to find minimum value, we use "min" function.
#Maximum value is
```{r, echo=FALSE}
maximumValue = max(myDataSet$X1)
maximumValue
```
#Minimum value is
```{r, echo=FALSE}
minimumValue = min(myDataSet$X1)
minimumValue
```
#f) The range is the subtraction of minimum value from the maximum value.
```{r, echo=FALSE}
rangeOfSet = maximumValue - minimumValue
rangeOfSet
```
#g) Comparison of range and standard deviation. #There are approximately
```{r, echo=FALSE}
howManySDInRange = rangeOfSet/sdFromFunction
howManySDInRange
```
#times standard deviation in range. According to relationship between SD and range, SD = R/4 in small samples and SD = R/6 in big samples which means our sample seems to be a big sample.
#h) Median can be found by using "median" function.
```{r, echo=FALSE}
medianOfSet = median(myDataSet$X1)
medianOfSet
```
#i) There is a special function which is "fivenum" to calculate five-num summary.
```{r, echo=FALSE}
fiveNumSummary = fivenum(myDataSet$X1)
fiveNumSummary
```
#j) We use "botplox" function for boxplots.
```{r, echo=FALSE}
boxplot(myDataSet$X1, horizontal = TRUE)
```
```{r, echo=FALSE}
```
#It seems there are outliers, also the data set is right skewed.
#l) I use "dotchart" function to draw dotplot.
```{r, echo=FALSE}
dotchart(myDataSet$X1, cex = 0.75, col="blue", main = "Dataset")
```
```{r, echo=FALSE}
```
#It seems data set is not mound shaped.
#m) No we can not because the data set is not regular, it is not normally distributed.

#n) No, we can not use Empirical Rule because the data set is not mound shaped.
#o) I used several functions to draw relative frequency histogram.
```{r, echo=FALSE}
h <- hist(myDataSet$X1, breaks = 100, plot=FALSE)
h$counts=h$counts/sum(h$counts)
plot(h, ylab="Relative Frequency", xlab = "My Data Set", main = "Relative Frequency Histogram of My Data Set")
```
```{r, echo=FALSE}
```
#p) Z-score can be found via formula "(number - mean)/standard deviation".
#Z-score of maximum value is
```{r, echo=FALSE}
zOfMax = (maximumValue - meanOfSample)/sdFromFunction
zOfMax
```
#Z-score of minimum value is
```{r, echo=FALSE}
zOfMin = (minimumValue - meanOfSample)/sdFromFunction
zOfMin
```
#If z-score is greater than 3 than the value is outlier, apparently maximum value is outlier.
